checkData

### 2023-08-25 analysis/checkData.Rmd
Update checkData.Rmd

Now check that when `exclusion_primary` is "RETAIN" `exclusion_reason` is NA.

```{r}
d_articles <- d_articles %>%
  mutate(exc_col_check = ifelse(exclusion_primary == "RETAIN" & is.na(exclusion_reason_primary), T, F)) # if we are retaining there should be an NA in the reason column

assert_that(all(d_articles$exc_col_check == F), msg = "Found unexpected value in exclusion reason column when it should be NA")
```

@@

```{r}
d_articles_random %>%
  count(exclusion_primary)
```

>>>>

Now check that when `exclusion_primary` and `exclusion_secondary` are "EXCLUDE" then we have reasons in the reason columns. When they are "RETAIN" the reason columns should be NA.

```{r}
# primary_exclusions <- d_articles %>% 
#   count(exclusion_primary, exclusion_reason_primary) %>%
#   mutate(expected_values = case_when(
#     exclusion_primary == "RETAIN" & is.na(exclusion_reason_primary) ~ T,
#     exclusion_primary == "EXCLUDE" & exclusion_reason_primary %in% c("NO ACCESS", "NON-ENGLISH", "NOT EMPIRICAL", "RETRACTED", "IS ITSELF PPC", "OTHER") ~ T,
#     TRUE ~ "criteria not met"
#   ))
# 
# secondary_exclusions <- d_articles %>% 
#   count(exclusion_secondary, exclusion_reason_secondary) %>%
#   
# 
# 
# assert_that(, msg = "Found unexpected value in exclusion reason column when it should be NA")
```

@@

```{r}
d_articles %>%
  count(exclusion_primary, exclusion_secondary)
```

Random ID 37 — TEH decides to go with primary coder and retain.
Random ID 41 - TEH decides to go with primary coder and retain.
Random ID 68 - TEH decides to go with secondary coder and exclude.
Random ID 95 - TEH decides to go with secondary coder and retain.
Random ID 103 — TEH decides to go with primary coder and exclude.
Random ID 120 — TEH decides to go with primary coder and retain.

```{r}
d_articles %>%
  filter(exclusion_primary != exclusion_secondary)
```
